Figs for public health journal article April 2017

### 2017-04-24 inst/documents/pub_health_j/pub_health_j_figs.Rmd
paper writing

```{r Fig5, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Influence of insecticide effectiveness and exposure on time-to-resistance for mixtures and sequences. Exposure to the insecticides is increased from row 1 (A and B) to row 2 (C and D). The effectiveness of one insecticide is increased from column 1 (A and C) to column2 (B and D). On the upper X axis 's' and 'm' indicate where the 50 percent resistance threshold is reached for the sequence and the mixture. In the lower right of each panel the the ratio of time-to-resistance for mixture/sequence is shown rounded to 1 decimal place to give an indication of the relative performance of mixtures and sequences.  A. All control inputs equal at 0.5 : time-to-resistance is longer for sequential use, B. Effectiveness of insecticide1 increased from 0.5 to 0.8 : time-to-resistance is longer for the mixture, C. Exposure increased to 0.8 : time-to-resistance is longer for sequential use, D. Effectiveness of insecticide1 and exposure increased to 0.8 : time-to-resistance equal for mixture and sequence. Increasing effectiveness increases times-to-resistance for mixtures and improves their performance relative to sequences. Increasing exposure decreases times-to-resistance for mixtures and reduces their performance relative to sequences. "}

#4 panel figure looking at effectiveness and exposure

#test of rearranging figures on a grid
#eff1  0.5  0.8
#exp
#0.5    1   2
#0.8    3   4

#layout(matrix(1:4,2,2, byrow = TRUE))

#add lower panel for legend
#layout(matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.5), respect=FALSE)

#layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )
#layout.show(n=5)

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#effectiveness on mixture

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

@@

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

@@

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('exposure = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#exposure 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

mtext('C.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1  and  expos 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.8 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

mtext('D.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

@@

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

@@

```{r Fig6, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Influence of the effectiveness of both insecticides on time-to-resistance for mixtures and sequences. Effectiveness of insecticide 2 is increased from row 1 (A and B) to row 2 (C and D). The effectiveness of insecticide 1 is increased from column 1 (A and C) to column2 (B and D). The 's' and 'm' on the upper X axis and 'mix/seq' in the lower right of each panel stand for sequence and mixture and are explained in the legend to Fig 5. A. Effectiveness of insecticide1 increased from 0.5 to 0.8, B. Effectiveness of insecticide1 increased from 0.5 to 1, C. Effectiveness of insecticides 1 and 2 increased to 0.8, D. Effectiveness of insecticide2 0.8 and of insecticide1 1. With the effectiveness of at least one insecticide greater than or equal to 0.8, times-to-resistance are longer for the mixture in all scenarios."}

#4 panel figure looking at effectiveness changes alone

#test of rearranging figures on a grid
#eff1  0.8  1
#eff2
#0.5    1   2
#0.8    3   4

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2 = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 1 eff2 0.5
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 1 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness2 = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 0.8 eff2 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

mtext('C.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 1 eff2 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 1 , phi.SS2_0B = 0.8 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

mtext('D.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 1', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

```{r Fig7, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Influence of dominance and resistance restoration on time-to-resistance for mixtures and sequences. Dominance of the allele coding for resistance to insecticide 1 is increased from row 1 (A and B) to row 2 (C and D). Resistance restoration for the allele coding for resistance to insecticide 1 is increased from column 1 (A and C) to column2 (B and D). The 's' and 'm' on the upper X axis and mix/seq in the lower right of each panel stand for sequence and mixture and are explained in the legend to Fig 5. A. All control inputs equal at 0.5, B. Resistance restoration for insecticide1 increased from 0.5 to 0.8, C. Dominance for insecticide1 increased to 0.8, D. Resistance restoration and dominance for insecticide1 increased to 0.8. Changing dominance and resistance restoration does not change the relative ordering of mixtures and sequences, time-to-resistance remains longest for sequences in all 4 scenarios."}

#4 panel figure looking at dominance and resistance restoration

#rr1  0.5  0.8
#dom1
#0.5    1   2
#0.8    3   4

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#testing
# plot(1)
# plot(1)
# plot(1)
# plot(1)

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1 = 0.5', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('dominance1 = 0.8', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#dominance1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

mtext('C.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#dom1 & rr1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.8 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.8 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 120, labelMixSeqRatio = 1 )

mtext('D.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('resistance restoration1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

```{r Fig8, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Influence of starting frequencies of resistance on time-to-resistance for mixtures and sequences. Starting frequency of the gene conferring resistance to insecticide 1 is decreased from row 1 (A and B) to row 2 (C and D). Effectiveness of insecticide 1 is increased from column 1 (A and C) to column2 (B and D). The 's' and 'm' on the upper X axis and mix/seq in the lower right of each panel stand for sequence and mixture and are explained in the legend to Fig 5. A. All control inputs equal at 0.5, starting frequencies of resistance at 0.01, B. Effectiveness for insecticide1 increased from 0.5 to 0.8, C. Starting frequency of resistance for insecticide1 decreased from 0.01 to 0.001, D. Effectiveness for insecticide1 increased from 0.5 to 0.8 and starting frequency for insecticide1 decreased from 0.01 to 0.001. In these scenarios the starting frequencies do not change better performance of sequences at low effectiveness and mixtures at high effectiveness."}

#4 panel figure looking at effectiveness and starting freq.

#eff1  0.5  0.8
#strt freq1
#0.01    1   2
#0.001    3   4

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1 = 1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('frequency1 = 0.1%', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#freq1 0.001
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

mtext('C.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#freq1 0.001, eff1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.001 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

mtext('D.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

```{r Fig 9 cost of 1 resistance, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Influence of cost of resistance on time-to-resistance for mixtures and sequences. Row 1 (A and B) same as Fig. 5 with no cost of resistance, row 2 (C and D) cost of resistance set to 0.15 with dominance of cost set to 0.5. The 's' and 'm' on the upper X axis and mix/seq in the lower right of each panel stand for sequence and mixture and are explained in the legend to Fig 5. The increase in cost of resistance from A. to C. removes the advantage of sequence relative to mixture. The ratio of time-to-resistance for the mixture divided by that for the sequence goes from 0. to 1. Costs seem to favour mixtures in these plots. Also be aware that costs would lead to a decline in the frequency of resistance for the first insecticide in a sequence when it stops being used."}

#4 panel figure looking at effectiveness and exposure

#test of rearranging figures on a grid
#eff1  0.5  0.8
#exp
#0.5    1   2
#0.8    3   4

#layout(matrix(1:4,2,2, byrow = TRUE))

#add lower panel for legend
#layout(matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.5), respect=FALSE)

#layout( matrix(c(1,2,3,4,5,5),3,2, byrow = TRUE), heights=c(1,1,0.2), 
# respect=matrix(c(1,1,1,1,0,0),3,2, byrow = TRUE) )
#layout.show(n=5)

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

#effectiveness on mixture

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('cost 1 = 0', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#base scenario

par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#effectiveness1 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = FALSE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1 )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('cost 1 = 0.15', line= -2, side=2, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 4, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#exposure 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.5 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = TRUE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1, z.RR1_00 = 0.15 )

mtext('C.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

#plot margins
par(mar=c(1.5, 0, 2, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1  and  expos 0.8
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = TRUE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 150, labelMixSeqRatio = 1, z.RR1_00 = 0.15  )

mtext('D.',side=3, adj=0, line=1, cex=0.9) #side=1b,2l,3t,4r

# legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide1 in mix   ", "insecticide2 alone   ", "insecticide2 in mix   "), col=c("red","red","blue","blue"), lty=c(2,1,2,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#add for when insecticides same
legend( 'bottom', legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   ", "insecticides1&2 in mix   "), col=c("red","blue","red","blue","purple"), lty=c(2,2,1,1,1), pch=c(NA,NA,NA,NA,NA), bty="n", cex=0.7, horiz =TRUE )

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.5', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

#label
par(mar=c(0, 0, 0, 0), pty='m') #b,l,t,r default c(5, 4, 4, 2)
plot( 0, type="n", axes=FALSE, ann=FALSE, pty='m')
mtext('effectiveness1 = 0.8', line= -2, side=1, cex=0.9) #side=1b,2l,3t,4r

>>>>

```{r Fig5, eval=TRUE, echo=FALSE, fig.height=7, fig.width=7, fig.show='hold', fig.align='left', fig.cap="Comparing time-to-resistance for mixtures and sequences  A. Resistance arises slower for the mixture, B. Resistance arises slower for the sequence. All inputs set to 0.5 except for starting frequency of resistance set to 0.01, and effectiveness of insecticide 1 set to 0.4 in A and 0.8 in B."}

#2 panel fig A. sequence better, B. mix better

#eff1  0.4  0.8

# add side panels for labels
#layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )

layout( matrix(c(1:2,3,3),2,2, byrow = TRUE), heights=c(1,0.15), widths=c(1,1) )
#layout.show(n=3)

#eff1 0.4 seq better

#plot margins, hight t just a bodge to get graphs down closer to legend
par(mar=c(1.5, 4, 15, 0)) #b,l,t,r default c(5, 4, 4, 2)

runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.4 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), xlabs = TRUE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 140, labelMixSeqRatio = 1 )

@@

#plot margins, hight t just a bodge to get graphs down closer to legend
par(mar=c(1.5, 4, 15, 0)) #b,l,t,r default c(5, 4, 4, 2)

#eff1 0.8 mix better
runcurtis_f2( max_gen=500,  P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.5 , h.RS2_0B = 0.5 , exposure = 0.5 , phi.SS1_A0 = 0.8 , phi.SS2_0B = 0.5 , rr_restoration_ins1 = 0.5 , rr_restoration_ins2 = 0.5 , addCombinedStrategy = FALSE, strategyLabels = c('s','','a','m'), ylab="", ylabs = FALSE, xlabs = TRUE, cex.axis = 0.8, addLegend=FALSE, main='', maxX = 140, labelMixSeqRatio = 1 )

@@

@@

legend( 'bottom', inset=0.1, legend=c("insecticide1 alone   ", "insecticide2 alone   ", "insecticide1 in mix   ", "insecticide2 in mix   "), col=c("red","blue","red","blue"), lty=c(2,2,1,1), pch=c(NA,NA,NA,NA), bty="n", cex=0.9, horiz =TRUE )

@@
